---
title: "Quality Control Report: export intelligence reports of Mark Hatcher"
author: "Ilkka Havukkala"

output: html_document
runtime: shiny
---

Peer review of this file: to do

The latest run and git merged version of this document is available at
[master repo](file:///P:/OTSP/export_intelligence/R/QC/Quality_Control_export_intelligence.html) 



```{r}
QC_rundate  # when R/QC/checks_QC.r was last run
```

The QC checks that PDF reports data corresponds to the TRED data and the Stat NZ data. Cross-checks also to UN comtrade website, e.g. 
[http://comtrade.un.org/db/mr/rfCommoditiesList.aspx?px=H1&cc=030211]

NB IMPORTANT TO ENSURE THAT ALL SCRIPTS HAVE BEEN REVIEWED.

Please **Agree** or **Disagree** that the QC is adequate, and thereby **Grant** or **Deny** permission to release the data for MBIE and/or public consumption. 


# Peer_reviews

```{r}
final
```

# Initial comments 

## Scope of each commodity summary page

The inputs/concordances/product_codes.csv file has the exact full codes used to make each summary report for Salmon, Chicken, Onions. NB some codes have 9 numbers, maybe leading zero missing, need to check carefully data matching.

inputs/concordances/readme.txt file states this list prepared by Andrew McCullum, but the process not detailed.

E.g. for Salmon, browsing at UN comtrade website 
[http://comtrade.un.org/db/mr/rfCommoditiesList.aspx?px=H1&cc=0302]

one can also find 

030211  Name: Trout, fresh or chilled, whole 
Description: Salmonidae

which is not included, although 

030219  Name: Salmonidae, not trout or salmon,fresh or chilled whole
Description: Salmonidae,

has been included in the product_codes.csv file, so the rationale of selection is not clear.

Same comment applies to the other commodities (not checked).

Also, not clear what code standard used. UN comtrade website has HS code revisions from 96 to 12 and SITC Rev.1 to Rev.4.
Link to code extracting this data from Stat NZ would be useful, as well as an URL to similar tables on STAT nz website.




# Basic checks 

## number of observations and variables

TO UPDATE

```{r}
str(final)
```



# Sample plots 

## Time series

image links here if needed, 
additionally plotted from Stat NZ and/or UN ComTrade for comparison


